---
title: "ECOL340_PrepDataset"
output: html_document
date: "2024-09-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## README

**Project and data** 

The intentiopn of this R Markdown is to prepare a dataset that Master Students of BatLab Norway part of the 2024-2025 academic year can use for ECOL340 exercises in the autumn of 2024. These datasets are made up of bat acoustic data automatically processed by Kaleidoscope Pro (v.5.6.3) with the Bats of Europe Classifier (v.5.4.0) modified to only include species included on the Norwegian National Red List. The data comes from sites CM-03, CM-07 (coastal monitoring sites), ST-01, and ST-02 (wind turbine sites at Stigafjellet wind farm) collected during the 2024 field season and includes only about a month of data collected around mid August from each site. Each observation (row) represents a 5 second (a few may be slightly shorter depending on the length of the original recording) acoustic recording (bat pass - though it may not contain a bat at all i.e., a noise file yet to be identified). Recordings that the classifier identifies as noise will be removed and treated as non-bat passes. We will then assume that the rest of the recordings do include bats, though false positives are likely without a manual acoustic analysis to verify these classifications. Mis-identification of bat species is also very likely and so this data cannot be treated as actual bat observations without further analysis. The objective of preparing this data is to give masters students experience working with bat acoustic datasets.


## Prepare work space
```{r}

library(data.table)
library(tidyverse)
library(beepr)
library(lubridate)
library(purrr)
library(janitor)
library(renv)
library(stringr)
library(beepr)


getwd()
# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/Documents/1. PhD_Main/GitHub_link/MSc_BatLab_2024-2025/MSc_BatLab_2024-2025"

```



```{r}

# Specify directories
# folders where csv files are all in for each site
inputCM03 <- "P:/SW_CoastalMonitoring/Data_process_auto_2024/CM-03/KPRO_08.08.2024_CM-03" 
inputCM22 <-"P:/SW_CoastalMonitoring/Data_process_auto_2024/CM-22/KPRO_13.08.2024_CM-22" 
inputST01 <-"P:/Noctur/DataCollection_2024/Acoustics/Stigafjellet/ST-01/WAV/KPRO_12.08.2024_ST-01" 
inputST02 <-"P:/Noctur/DataCollection_2024/Acoustics/Stigafjellet/ST-02/WAV/KPRO_12.08.2024_ST-02" 


output <- "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/Field Work 2024/ForMastersStudents"

file.name <- "ECOL340_CombineAutoIDs"

todays_date <- Sys.Date()
 
dir.name <- str_c(output,"/", file.name, "_", todays_date)
dir.name
 
output_today <- dir.name
output_today

dir.create(output_today)
output_today

# "C:/Users/apmc/OneDrive - Norwegian University of Life Sciences/BatLab Norway/Field Work 2024/ForMastersStudents/ECOL340_CombineAutoIDs_2024-09-13"

```


```{r}


CM03 <- list.files(path=inputCM03, pattern="id.csv", recursive = FALSE)
CM03

CM22 <- list.files(path=inputCM22, pattern="id.csv", recursive = FALSE)
CM22

ST01 <- list.files(path=inputST01, pattern="id.csv", recursive = FALSE)
ST01

ST02 <- list.files(path=inputST02, pattern="id.csv", recursive = FALSE)
ST02

# #To read all your csv files and create a list with all these elements

## CM-03
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file(inputCM03)))
getwd()

CM03_data <- lapply(CM03, read.csv)

## CM-22
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file(inputCM22)))
getwd()

CM22_data <- lapply(CM22, read.csv)

## ST-01
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file(inputST01)))
getwd()

ST01_data <- lapply(ST01, read.csv)

## ST-02
knitr::opts_chunk$set(
    root.dir = setwd(rprojroot::find_rstudio_root_file(inputST02)))
getwd()

ST02_data <- lapply(ST02, read.csv)



#To add the name of each csv in the list
names(CM03_data) <- gsub("//.csv$", "", CM03)
names(CM22_data) <- gsub("//.csv$", "", CM22)
names(ST01_data) <- gsub("//.csv$", "", ST01)
names(ST02_data) <- gsub("//.csv$", "", ST02)

#To create one single dataframe with all single dataframes
## Do yourself a favor - ADD A SITE COLUMN HERE! 
big_CM03 <- rbindlist(CM03_data, fill = TRUE)
big_CM03$Site <- "CM-03" 
dim(big_CM03)
# 20430    45
names(big_CM03)


big_CM22 <- rbindlist(CM22_data, fill = TRUE)
big_CM22$Site <- "CM-22" 
dim(big_CM22)
# 5948   45
names(big_CM22)


big_ST01 <- rbindlist(ST01_data, fill = TRUE)
big_ST01$Site <- "ST-01" 
dim(big_ST01)
# 1352   45
names(big_ST01)

big_ST02 <- rbindlist(ST02_data, fill = TRUE)
big_ST02$Site <- "ST-02" 
dim(big_ST02)
# 1191   45
names(big_ST02)

### I will now combine all of these into one large csv file but because of the differences in column numbers and also that these will each be organized separately, I am not sure how useful that CSV file is ... 

alist = list(big_CM03, big_CM22, 
             big_ST01, big_ST02)

big_data <- rbindlist(alist, fill=TRUE)
dim(big_data)
# 28921    45

# ## Uncleaned csv file of all AUTOIDS combined
#write.csv(big_data, file = file.path(output_today, "MSc_ECOL340_Subset_AllProcessedBatDataCombined.csv")) 
# # exported 13.09.2024


```

## Now create student specific subsets 

```{r}

df <- big_data %>% mutate(Site = factor(Site), AUTO.ID. = factor(AUTO.ID.)) 
summary(df$Site)
# CM-03  CM-22 ST-01 ST-02 
# 20430  5948  1352  1191

summary(df$AUTO.ID.) # No NAs, lots of Noise! 
# I will leave the Noise files in for now but you (the students) should remove them at some point if you want to use this to look at "bat" data. 

## for Sara
Sdf <- df %>% filter(Site %in% c("CM-03", "CM-22")) %>% droplevels()

summary(Sdf$Site)
# CM-03 CM-22 
# 20430  5948 

summary(Sdf$AUTO.ID.)

#write.csv(Sdf, file = file.path(output_today, "SARA_MSc_ECOL340_Subset_AllProcessedBatDataCombined.csv"))
# 13.09.2024

## for Ylva
Ydf <- df %>% filter(Site %in% c("ST-01", "ST-02")) %>% droplevels()

summary(Ydf$Site)
# ST-01 ST-02 
#  1352  1191 

summary(Ydf$AUTO.ID.)

# write.csv(Ydf, file = file.path(output_today, "YLVA_MSc_ECOL340_Subset_AllProcessedBatDataCombined.csv"))
# 13.09.2024


## for Benedikte
Bdf <- df %>% filter(Site %in% c("ST-01", "CM-03")) %>% droplevels()

summary(Bdf$Site)
# ST-01 ST-02 
#  1352  1191

summary(Bdf$AUTO.ID.)

# write.csv(Bdf, file = file.path(output_today, "BENEDIKTE_MSc_ECOL340_Subset_AllProcessedBatDataCombined.csv"))
# 13.09.2024

```

That's all for now
